---
title: "ESM 244 Assignment 2"
subtitle: "Parameter Estimation and Bootstrapping"
author: "Phoebe Racine"
date: "February 20, 2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library and Dataset, include = FALSE}
library(tidyverse)
fish_catch <- read_csv("~/Winter 2018 Classes/ESM 244/fish_catch.csv")
ca_pop <- read_csv("~/Winter 2018 Classes/ESM 244/ca_pop.csv")
ca_pest <- read_csv("~/Winter 2018 Classes/ESM 244/ca_pest.csv")

```


##Task 3: Parameter Estimation - Wild Fish Catch
Source: Wild fish catch and aquaculture production, compiled by Earth Policy Institute with 1950-2010 from U.N. Food and Agriculture Organization (FAO), Global Capture Production and Global Aquaculture
Production, electronic databases, at www.fao.org/fishery/topic/16140/en, updated March 2012; estimates for 2011 and projections for 2012 from FAO, Food Outlook (Rome: November 2012), p. 10.
- Download the data fish_catch.csv from GauchoSpace
- Find an equation with parameters estimated by nonlinear least squares for the increase in wild fish catch from 1950 - 2012. Hint: You might want to set 1950 = 0 (i.e., create a new column with years starting at 0, instead of value 1950, and use those values for your model.)
- Create a scatterplot graph of the data, with the predictive line based on the estimated parameters
What you will submit for this task:
(1) The final equation (with estimated parameters from NLS) describing the increase in wild fish catch
(2) Your finalized graph of the original data + predicted catch values based on the NLS parameter estimates. Include a figure caption.
```{r}
## Need to rows 1-4 and 68 onwards



```


##Task 4: Bootstrapped Confidence Interval for Proportions
The following data are from the 2014 UCSB Campus Climate Project Final Report (prepared by Rankin & Associates Consulting, available at http://campusclimate.ucop.edu/_common/files/pdf-climate/ucsb-fullreport.
pdf).
In the study, 22 of 36 surveyed UCSB community members (61%) identifying as genderqueer responded that
they had personally experienced "exclusionary, offensive, hostile or intimidating conduct" (compared to 26%
and 19% for those identifying as women and men, respectively).
Create a vector reflecting the collected survey data, then find the bootstrapped 95% confidence interval for
the proportion of genderqueer individuals experiencing exclusionary conduct based on the 2014 UCSB survey data.
Hint: this will require you to create a function that calculates the proportion of a specified outcome for each bootstrap sample.
What you will submit for this task:
(1) All of your code for Task 4 (preparing and knitting your assignment using RMarkdown would make this easy, but you can copy and paste into another editor if you want to.)
(2) The sampling distribution (a histogram) of bootstrapped proportions, finalized (formatting, labels, and appearance matters). Include a figure caption.
(3) A final statement describing the bootstrapped CI that would be suitable for publication.
```{r}



```
**Final Statement**

##Task 5: RProjects, RMarkdown, Data Wrangling and ggplot
- Download files ca_pest.csv (California pesticide application data by county) and ca_pop.csv (California
population and income data by county) from GauchoSpace.
Data sources:
. Pesticide data: 2014 CA pesticide application (by county) from the California Department of Pesticide Regulation (accessed at http://www.cdpr.ca.gov/docs/pur/pur14rep/14_pur.htm)
. California population & income data: U.S. Census Bureau. American Community Survey, 2010- 2014 American Community Survey 5-Year Estimates
Column information:
County: County name
PestPounds: Pounds of chemical active ingredient applied by county (annual, 2014)
StateRank: Statewide ranking by county (by pesticide amount applied, 1 = high)
CountyArea: County area (square miles)
Population: County population (based on 2010 - 2014 census data)
PCIncome: Per capita income
MedHouseIncome: Median household income ($)
MedFamilyIncome: Median family income ($)
a. Create a new project in R
b. Copy the data files into the folder where you created the new project - the files should then show up in your working directory in RStudio
c. Create a new RMarkdown file (in the project) in which you:
d. Load the tidyverse
e. Load the two datasets (remember, if they're in the working directory, you don't need the whole pathway in the read_csv function)
f. Merge the two data frames by matching character strings in the County columns
g. Create a new column for pesticide applied (pounds) per square mile
h. Sort the new data frame from highest to lowest by the pesticide (pounds) per square mile column you created in (g)
i. Keep only the columns for: county name, pesticide applied per square mile, median family income and population
j. Create a finalized bubble plot of median household income versus pesticide application per square mile, with the size of the 'bubbles' based on county population. Add a visual line of best fit (use geom_smooth, without an error ribbon - you do not need to actually find the model equation for this assignment). Add a label (county name) to the notable outlier on the graph. Include a figure caption.
What you will submit for this task:
(1) All of the code you wrote in your markdown document for Task 5 parts (d) - (j). The output for each line should not be included (i.e., if knitting in markdown use results = "hide" and/or message = FALSE in the code chunk header to suppress outputs as needed).
(2) Your finalized bubble plot, with a figure caption